Reproducibility of HCP pipelines across operating systems

### 2016-11-01 paper.tex
Added references

>>>>

The operating system is defined here as a consistent set of software
packages organized in a trusted repository.

The operating system is not the only part of the computational
environment that may hamper reproducibility. The work
in~\cite{diethelm2012limits} mentions reproducibility issues coming
from parallelization.

Reproducibility has several other aspects, see, e.g.,
\url{https://medium.com/@lorenaabarba/barba-group-reproducibility-syllabus-e3757ee635cf#.ty3zmgd4k}/
